---
title: "Analysis score J.C.Staff"
author: "Thammarat Kowitkanit"
date: "10/7/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

This paper will analyze J.C.Staff studio dataframe about relationship between score, genres, type of aired, episode and source variables.

- explore data
- descriptive analysis


## Explore data
```{r echo=FALSE ,warning=FALSE,message=FALSE}
library(tidyverse)
jc <- read.csv("J.C.Staff dataset.csv", stringsAsFactors =FALSE)

knitr::kable(head(jc , 10), format = "latex")

jc$Score <- replace(jc$Score,jc$Score == "Unknown", NA)
jc$Score <- as.numeric(as.character(jc$Score))
```


> Table 1 : show headers of anime made by J.C.Staff

## Descriptive analysis

### 1.Score and Genres

```{r echo=FALSE ,warning=FALSE,message=FALSE}
  
 
  jc_action <- jc %>% select("Genres" , "Score") %>%
                  filter(grepl("Action", Genres))
  jc_comedy <- jc %>% select("Genres" , "Score") %>%
                  filter(grepl("Comedy", Genres))
  jc_drama <- jc %>% select("Genres" , "Score") %>%
                  filter(grepl("Drama", Genres))
  jc_fantasy <- jc %>% select("Genres" , "Score") %>%
                  filter(grepl("Fantasy", Genres))
  ##transform column chracter score to numeric score
  
  
  ##plot graph
  
  jc_action %>% ggplot(aes(Score)) + 
                geom_histogram(bins = 4) +
                theme_minimal()
  
```

> Fig 1 : Histogram of score that represent action anime 

```{r echo=FALSE ,warning=FALSE,message=FALSE}

   jc_fantasy %>% ggplot(aes(Score)) + geom_histogram(bins = 10)+
                   theme_minimal()
```

> Fig 2 : Histogram of score that represent fantasy anime 

```{r echo=FALSE ,warning=FALSE,message=FALSE}

   jc_comedy %>% ggplot(aes(Score)) + geom_histogram(bins = 10)+
                  theme_minimal()

```

> Fig 3 : Histogram of score that represent comedy anime 

```{r echo=FALSE ,warning=FALSE,message=FALSE}

   jc_drama %>% ggplot(aes(Score)) + geom_histogram(bins =10)+
                theme_minimal()

```

> Fig 4 : Histogram of score that represent drama anime 


```{r echo=FALSE ,warning=FALSE,message=FALSE}
##create dataframe that contain mean score
Genres <- c("action" , "fantasy" , "comedy" , "drama")
Mean <- c( round( mean(jc_action$Score, na.rm = TRUE), digits = 2 ), 
          round(mean(jc_fantasy$Score, na.rm = TRUE), digits = 2 ),                      round(mean(jc_comedy$Score, na.rm = TRUE), digits = 2 ), 
          round(mean(jc_drama$Score, na.rm = TRUE), digits = 2 ) )

table_generes <- data.frame(Genres, Mean)
knitr::kable(table_generes )

```

> table 2 : mean of score each generes anime

From histogram and mean table we can summary that J.C.Staff can better make comedy and drama anime than action and fantasy anime. 

### 2.Score and Type of aired

```{r echo=FALSE ,warning=FALSE,message=FALSE}
  jc_TV <- jc %>% filter(grepl("TV", Type))
  
  jc_TV %>% ggplot(aes(Score)) + geom_histogram(bins = 4) + theme_minimal()

```

> Fig 5 : histogram of score that represent TV anime

```{r echo=FALSE ,warning=FALSE,message=FALSE}
  jc_Movie <- jc %>% filter(grepl("Movie", Type))
  
  jc_Movie %>% ggplot(aes(Score)) + geom_histogram(bins = 5) + theme_minimal()

```

> Fig 6 : histogram of score that represent Movie anime

```{r echo=FALSE ,warning=FALSE,message=FALSE}
  Aired <- c("TV" , "Movie")
  Aired_Mean <- c(round(mean(jc_TV $Score, na.rm = TRUE), digits = 2), 
                  round(mean(jc_Movie$Score, na.rm = TRUE), digits = 2) )

  table_generes <- data.frame(Aired, Mean = Aired_Mean)
  knitr::kable(table_generes )

```

> table 3 : mean of score each type of aired anime

From histogram and mean table we can summary that TV anime has better score than Movie anime. 

### 3.Score and amount of episode

```{r echo=FALSE ,warning=FALSE,message=FALSE}
  jc_oneseason <- jc %>% filter(Episodes == 12 | Episodes == 13)
  
  
  
  jc_oneseason %>% ggplot(aes(Score)) + geom_histogram(bins = 4) +                                theme_minimal()

```

> Fig 7 : histogram of score that represent one season anime

```{r echo=FALSE ,warning=FALSE,message=FALSE}
  jc_twoseason <- jc %>% filter(Episodes == 24 | Episodes == 25 | 
                                  Episodes == 26)
  jc_twoseason %>% ggplot(aes(Score)) + geom_histogram(bins = 5) +                                theme_minimal()

```

> Fig 8 : histogram of score that represent two season anime

```{r echo=FALSE ,warning=FALSE,message=FALSE}
  Season <- c("One season anime" , "two season anime")
  Season_Mean <- c(round(mean(jc_oneseason$Score, na.rm = TRUE), digits = 2), 
                  round(mean(jc_twoseason$Score, na.rm = TRUE), digits = 2) )

  table_generes <- data.frame(Season, Mean = Season_Mean)
  knitr::kable(table_generes )

```

> table 4 : mean of score each season anime

From histogram and mean table we can summary that J.C.Staff can better make one season anime than two season anime.

### 4.Score and Source


```{r echo=FALSE ,warning=FALSE,message=FALSE}
  jc_Manga <- jc %>% filter(grepl("Manga", Source))
  
  
  jc_Manga %>% ggplot(aes(Score)) + geom_histogram(bins = 5) + theme_minimal()

```

> Fig 9 : histogram of score that represent manga anime

```{r echo=FALSE ,warning=FALSE,message=FALSE}
  jc_novel <- jc %>% filter(grepl("Light novel", Source))
  jc_novel %>% ggplot(aes(Score)) + geom_histogram(bins = 5) + theme_minimal()

```

> Fig 10 : histogram of score that represent Light novel anime

```{r echo=FALSE ,warning=FALSE,message=FALSE}
  jc_original <- jc %>% filter(grepl("Original", Source))

  jc_original %>% ggplot(aes(Score)) + geom_histogram(bins = 7) + theme_minimal()

```

> Fig 11 : histogram of score that represent Original anime

```{r echo=FALSE ,warning=FALSE,message=FALSE}
  jc_game <- jc %>% filter(grepl("Game", Source))
  jc_game %>% ggplot(aes(Score)) + geom_histogram(bins = 5) + theme_minimal()

```

> Fig 12 : histogram of score that represent game anime

```{r echo=FALSE ,warning=FALSE,message=FALSE}
##create dataframe that contain mean score
Source <- c("Manga" , "Light novel" , "Original" , "Game")
Source_Mean <- c( round( mean(jc_Manga$Score, na.rm = TRUE), digits = 2 ), 
          round(mean(jc_novel$Score, na.rm = TRUE), digits = 2 ),                      round(mean(jc_original$Score, na.rm = TRUE), digits = 2 ), 
          round(mean(jc_game$Score, na.rm = TRUE), digits = 2 ) )

table_generes <- data.frame(Source, Mean = Source_Mean)
knitr::kable(table_generes )

```


> table 5 : mean of score each source anime

From histogram and mean table we can summary that J.C.Staff can better make light novel anime, manga anime, Original anime and game anime sequentially.
